Secure Composition of Robust and Optimising Compilers

### 2023-07-05 popl/main.tex

\section{Background: Security Properties and Secure Compilers\pages{1}}\label{sec:background}

To introduce the security argument of this paper, this section first presents the concepts of (security) properties, of their satisfaction, and of their robust satisfaction (i.e., satisfaction in the presence of an active attacker; \Cref{subsec:bg:tprop}).
Then, borrowing from existing work~\cite{abate2019jour,abate2021extacc,patrignani2021rsc}, the section introduces secure compilers as compilers that preserve robust property satisfaction (\Cref{subsec:bg:rtp}).

\subsection{Properties and (Robust) Satisfaction}\label{subsec:bg:tprop}

% The intuition behind security is that nothing bad happens.
% \MPin{
% 	no: that is safety
% }
This paper employs the security model where programs are written in a language whose semantics emits events $\event$.
Events include security--relevant actions (e.g., reading from and writing to memory) and the unobservable event $\emptyevent$.
As programs executes, their emitted events are concatenated in traces ($\trace$), which serve as the description of the behaviour of a program.%
\footnote{
Throughout the paper, we denote empty sequences with $\hole{\cdot}$ and concatenate sequences $\trace[_{1}],\trace[_{2}]$ as $\trace[_{1}]\cdot\trace[_{2}]$.
Prepending elements to sequences uses the same notation: $\event\cdot\trace$.
}

>>>>

\section{Background: Security Properties and Secure Compilers\pages{1}}\label{sec:background}
To introduce the security argument of this paper, this section first presents the concepts of (security) properties, of their satisfaction, and of their robust satisfaction (i.e., satisfaction in the presence of an active attacker; \Cref{subsec:bg:tprop}).
Then, borrowing from existing work~\cite{abate2019jour,abate2021extacc,patrignani2021rsc}, the section introduces secure compilers as compilers that preserve robust property satisfaction (\Cref{subsec:bg:rtp}).

\subsection{Properties, Satisfaction, and Robust Satisfaction}\label{subsec:bg:tprop}

% The intuition behind security is that nothing bad happens.
% \MPin{
% 	no: that is safety
% }
This paper employs the security model where programs are written in a language whose semantics emits events $\event$.
Events include security-relevant actions (e.g., reading ad writing to memory) and the unobservable event $\emptyevent$.
As programs executes, their emitted events are concatenated in traces ($\trace$), which serve as the description of the behaviour of a program.%
\footnote{
Throughout the paper, we denote empty sequences with $\hole{\cdot}$ and concatenate sequences $\trace[_{1}],\trace[_{2}]$ as $\trace[_{1}]\cdot\trace[_{2}]$.
Prepending elements to sequences uses the same notation: $\event\cdot\trace$.
}
